Type-Safe Modular Parsing

### 2016-11-29 paper/sections/RelatedWork.tex
minor comment

Some more recent papers [Packrat 2006, parsing with derivatives 2011, parser combinator for ambiguous left-recursive grammars] proposed a series of novel parsing techniques, moreover, they did put an eye on the issue of left-recursion. As we explained before, we have selected Packrat Parsing for our prototype implementation, as the combinators are convenient to use in Scala, which is a platform where functional laziness and Object Algebras can perfectly coexist. Also, its support for direct left-recursion is already helpful for designing real-world parsers practically, though [packrat parsing can support left recursion] further demonstrated that general left-recursion is supported from the theoretical point of view. We have also mentioned that the components used in our library can have alternatives, for instance, a different set of parser combinators may support ambiguous and left-recursive grammars, or be applicable to a different subset of context-free grammars or more, or even lead us to another level of performance.

>>>>

Some more recent papers [Packrat 2006, parsing with derivatives 2011, parser combinator for ambiguous left-recursive grammars] \haoyuan{Pracitical, general parser combinators?} proposed a series of novel parsing techniques, moreover, they did put an eye on the issue of left-recursion. As we explained before, we have selected Packrat Parsing for our prototype implementation, as the combinators are convenient to use in Scala, which is a platform where functional laziness and Object Algebras can perfectly coexist. Also, its support for direct left-recursion is already helpful for designing real-world parsers practically, though [packrat parsing can support left recursion] further demonstrated that general left-recursion is supported from the theoretical point of view. We have also mentioned that the components used in our library can have alternatives, for instance, a different set of parser combinators may support ambiguous and left-recursive grammars, or be applicable to a different subset of context-free grammars or more, or even lead us to another level of performance.
